\Large\textbf{Decentralized Data Marketplace to Enable Trusted Machine Economy}

### 2019-09-14 paper.tex
Grammar tweak and component MAM rearrangement

\maketitle
\section*{\normalsize\textbf{Abstract}}
Data as a Service (DaaS) has been offering consumption data, geographic information, etc., for a number of years and has evolved into a multi-billion dollar industry. But IoT cannot be considered a mere extension of DaaS. Transacting IoT data must be different in many respects in order to build much-needed trust in IoT-enabled data marketplaces, trust that will be key to their sustainability. Data generated internally to an organization is usually not enough to remain competitive, enhance customer experience, and improve strategic decision-making.

In this paper, we propose a novel approach to construct IoT-enabled data marketplace by means of decentralized and trustless architecture, posting the trade records but also including the transaction process on the distributed ledgers. This way can efficiently enhance the degree of transparency, since all interactions with smart contracts will be written on-chain. In other words, users transport the encrypted data audited by smart contracts for storage via an end-to-end encrypted message channel which allows emitting and accessing trusted data stream over the distributed ledger regardless of the size or cost of the device, simultaneously making a verifiable Auth-compliant request to the platform. Later, the verified data will enter the data marketplace to be traded. Furthermore, the platform will complete matching, trading and refunding process without the human intervention which also protects the rights of data providers and consumers through a trading policy written on the smart contract, and finally apply evolutionary game theory to the machine economy.

\begin{IEEEkeywords}
    streaming data, crowd sensing, data marketplace, decentralization
\end{IEEEkeywords}

\section{\normalsize\textbf{Introduction}}
The growth of data marketplaces is an inevitable result of the IoT (Internet of Things) revolution. As physical assets such as ships, factories, vehicles, farms or buildings become digital, their digital twins will gradually act as secure data exchanges.\cite{digitaltwin}\cite{AutonomousDriving} As data streams surge across silos and carry value across organizations, traditional value chains will transition into a web of value. This paradigm will be more complex to administer, forcing business to rethink their competitive play as part of these ecosystems. Data marketplaces will emerge as a means to exchange data, monetize data streams and provide the basis of new business models. We refer to this new wave of value creation, for the Internet of Everything, as the "Economy of Things." There are three main barriers to achieving data marketplace:
\begin{enumerate}
    \item Data owners do not have much control over their data and their data are locked in silos managed by products and services companies.
    \item Data owners only have access to their own data which has little value when it comes to knowledge discovery.
    \item Data owners do not know how to discover knowledge from raw data.
\end{enumerate}

To overcome these barriers, we implement IoT-enabled Data Marketplace and sensor data submission functionalities are intended to be very lightweight, capable of running on embedded devices. They will only need to perform Tangle operations (e.g., producing and consuming secure channels) and communicate with decentralized facilities, which do not rely on single-source network infrastructure. This proposed reference architecture includes functions that could be mapped to different stakeholders, and multiple functions can be implemented by the same administrative stakeholder in a given operational deployment.
\begin{enumerate}
    \item Data Sellers are entities that deploy an IoT infrastructure, for example smart energy meters. These entities are interested in selling the collected data or subsets of that data.
    \item Managed Data Lakes would typically store a massive amount of data and metadata to enable data discovery.
    \item Data Buyers consuming data streams or downloading data sets are interested in the additional value that external data can bring to their internal data.
\end{enumerate}

Take the use case of Airbox\cite{LASS} for instance. Every household with Airbox can collect air quality records automatically and autonomically, rather than passively accept the outcomes from the centralized authorities. To protect privacy, data should be encrypted before on-chain. As for the data reliability, we extended the backbone design of Airbox to interoperate the smart-contract-oriented structure to write down every transaction. At the same time, data on-chain will send a verifiable request to mark itself as "being tradeable." This step enables buyers to review and bargain at will. Last but not least, payments will be stored on the smart contracts until the transactions are confirmed. The whole sequence is illustrated in Figure \ref{fig:airbox}.

@@

\section{\normalsize\textbf{Related Work}}
The economic value of huge amount of data emerges, several researchers have started to explore the design of data marketplace. The Third Party Auditors (TPAs)-based frameworks\cite{TPA} is far from being satisfactory due to the unstandardize data format dynamic nature of IoT data. Therefore a decentralized data integrity validation and trading process has been proposed recent years, and distributed ledger technology (DLT) is considered a solution, which has the immutable data storage feature that the existence of data can be trusted and no longer rely on any third party authority.

Data Integrity as a Service (DIaaS) is a blockchain based framework for data integrity proposed by Liu et al.\cite{DIaas} which is a Cloud Server Service (CSS) allows both data provider and consumer to validate data integrity by comparing hashes on Ethereum smart contract\cite{smartContract} and Cloud Server. Moreover, Ethereum smart contract can also realize the purchase agreement, including authoriziation and the penalization. However, the architecture of DIaaS needs highly trust on CSS, if CSS is malicious or crashed, that will cause losses to both providers and consumers. Also, the performance analysis shows that IoT devices have low efficiency interacting with Ethereum due to the time-consuming Proof-of-Work(PoW) process.

By solving the inefficiency of the Blockchain, \textbf{IOTA}\cite{IOTAwhitepaper} is a cryptocurrency for the IoT industry based on a revolutionary distributed ledger technology, the \textbf{Tangle}, which enables zero-transaction. On top of that, \textbf{Masked Authenticated Messaging(MAM)}\cite{MAM}, a second layer data communication protocol which allows to emit, access and verify an encrypted data stream over the Tangle where privacy and integrity meet.

On the basis of the Tangle and MAM, IOTA foundation launched a Data Marketplace\cite{IOTADataMarket} which is suitable for IoT streaming data that not only allows data providers to put data on Tangle without any trusted cloud services, but also allow providers and consumers to trade on Tangle and protect privacy and assure data integrity from source with MAM. Nevertheless, the platform design is centralized, new devices require manual approval from IOTA foundation to be visible in the marketplace. Also, interacting with Tangle is still the bottleneck for low-level devices especially in an unstable network or electricity environment.

A different framework design proposed by Gupta, S.Kanhere and Jurdak\cite{3tierDataMarket} could reduce the burden of low-level devices as mentioned. The infrastructure is a 3-tier decentralized data marketplace architectural design with Ethereum smart contract which consists of provider, consumer and broker. Where broker is a trustless and highly resourced device that will facilitate the trading of data between the consumer and providers. However, the data integrity and authentication of each participant are still future work.

The sustainability of IoT economic system is under discussion by Dusit Niyato et al.\cite{UtilityStruct}. They evaluated the utility structure of data trading and presented game theory model.  Data marketplace organizers can determine their policies to ensure a sustainable system with the Nash Equilibrium found by game theory and the utility structure. However, refund and subscription economy were not mentioned in their work.

The previous work proposed different solution to specific issues of data marketplace. In this paper, we had an  overall design of decentralized data marketplace that takes care of data integrity and trading procedure such as buyout and subscibing to future data on distributed ledger.

\section{\normalsize\textbf{System Architecture}}
Our proposed data marketplace framework is a 3-tier decentralized architecture with a registrar who is responsible for marketplace registration in order to put participants' information on distributed ledgers for validation, data providers who publish data, data consumers who search for interested products and issue a new trade, and brokers who interact between data providers and consumers, including data publishing, product metadata generation and trading process.

@@

\subsubsection{Registrar}
The registrar is responsible for creating a Registration Contract, which maintains a lookup table of participants, and has the authority to control the participant lists of the decentralized data marketplace.

@@

\subsubsection{Consumer}
Consumers aspire to obtain streaming data to promote the value of their service. However, it is a big challenge for most consumers to collect the desired data by themselves. So they look forward to purchasing the streaming data from data providers.

\subsubsection{Broker}
Brokers represent data providers and consumers to do computing tasks since brokers are expected to have higher resource. Some trustworthy brokers who pass procedures for conformity assessment are added to the decentralized data marketplace. Once a qualified data provider requests to launch a new product, the broker is requested to deal with the trading process and publish the provider’s data streams to the MAM channel. For each product, brokerage fees will be charged by the broker.

@@

\subsection{Components}
\subsubsection{Masked Authenticated Messaging}
IOTA\cite{IOTAwhitepaper} is a feeless and scalable cryptocurrency while MAM is the second layer data communication protocol built on top of Tangle.

MAM resolves the challenge to publish encrypted streaming data to distributed ledgers. It publishes messages encrypted with a \textbf{session key} to \textbf{channel}, which is a form of transactions that each address can be derived from the previous one. Therefore, with \textbf{channel root}, the first message of a channel, and the session key, all data on the channel is accessible.

One can create multiple channels as possible, however, the size of a channel is fixed which is decided before creation, thus data providers should decide how to distribute data product into MAM channels. While the creation of a MAM channel is time-consuming, brokers are also responsible for channel creation, encrypted data publishing and session key certification in our system. See Figure \ref{fig:launching_product}

@@

\subsubsection{TangleID}
TangleID\cite{TangleID} is a self-soverign identity system based on IOTA that do not require any third-party authority to verify an identity and its digital footprint. In TangleID, the digital footprint is converted into digital assets with the principle of Decentralized Identifiers (DIDs)\cite{DID} defined by W3C, and by putting DID documents on MAM makes TangleID a GDPR-Complianced system. With every participant in data marketplace registers on TangleID, one can easily verify data providers' identity to ensure the data persistency from data sources.

\subsubsection{Ethereum Smart Contract}
Smart contract is a protocol for formulating agreement on blockchain that provides verification and execution of the contract. The code in the smart contract could interact with other contracts, make decisions, store data and transfer cryptocurrency. All conditions and states established in the contract are transparent and with enforcement. The appearance of smart contracts makes trading more flexible, and achieves more complex trading patterns in reality.

\subsubsection{Blind Signature}
 It is a risk revealing session keys to brokers since contents may be copied by brokers, which causes data providers' loss. Therefore, Blind signature is used to prevent the situation. Blind signature\cite{blindSig} is a form of digital signature where the message is first "blinded" by a random "blinding factor", then passed to a signer to sign. The resulting message, along with the blinding factor, can be later verified with the signer's public key. In our system design, brokers would perform blind signature during the process of adding new products for data providers, in order to send the secret key of MAM channel to smart contract without knowing it.

\subsubsection{IPFS}
Inter-Planetary File system(IPFS)\cite{IPFS} is a peer-to-peer network for storing and accessing files, websites, applications, and data in a distributed file system which is not maintained with certain nodes or entities but all IPFS users. In our proposed architecture, brokers are responsible to publish the metadata of products, including title, data provider information and data preview to IPFS in order to provide users with search capabilities to meet the consumers' need.

\section{\normalsize\textbf{Trading Model}}
In the following, we describe the data trading process in detail and we would use game theory to ensure the sustainability of our tading model. To participate a data marketplace, data providers and consumers have to register first. Then data provider can launch its product on the marketplace. Once a product is launched, it is searchable and could be traded afterward. The whole trading and refunding process is defined in smart contracts which are easily traceable and irreversible.

The consumer will pay for the data, only when the data sold by the data provider with high enough quality/accuracy, which we called these data as decent data.
Once the accuracy is lower than a certain threshold, which we called these data as unacceptable data, the consumers would consider this data provider as a low quality data provider, and stop buying data from this data provider.

Refund is a major issue in our research. However, we don't have to take refund as a factor in our game theory model, since in our decentralized data marketplace we use smart contract to store the subscription fee which will be paid to buy the future data. The subscription fee will be paid as new data is transmitted to consumers. In other words, data provider doesn't need to take any procedure to transfer subscription fee from his/her own account to consumers' account. For the same reason, data provider has no responsibility on the refunding processing fee charged by the smart contract as well.

\subsection{Participants Registration}
At the beginning, the registrar creates a Registration Contract, which maintains all participants' information, including their DID documents and public keys. Everyone can query participants' public keys. Those who would like to sell or purchase data may register to become the data providers or consumers. The registrar has the authority to agree with applications. After that, their identities are available in the Registration Contract and launching and trading processes can be started.

\subsection{Launching and Searching Products}
To sell the streaming data, a data provider has to launch a new product on the data marketplace in advance as shown in Figure \ref{fig:launching_product}. The data provider determines a trusted broker and asks the broker to create a new MAM channel and Product Contract. Each product has a Product Contract to record the participants, subscription price brokerage fee, quantity of data and  trading process.

Brokers certify session keys as well. Only one session key can be signed in each product, so data providers can't fake a session key to deceive consumers. Figure \ref{fig:key_certification} shows the certification process. When a data provider asks a broker to ceritfy new session key $k$, the data provider uses the broker's public key, which is available in the Registration Contract after the broker's registration, as a blinding factor, and the session key is blinded. Then the data provider sends the blinded session key $Blind(k)$ to the broker. The broker signs the message and returns the signature $Sign(Blind(k))$ to data provider. The data provider removes the blinding factor and obtains the broker's signature of the session key, $Sign(k)$, which is verifiable by consumers.

@@

The contract address and product description will be stored in a file which is uploaded to IPFS. Consumers can search the desired product by keywords or tags. The consumer then evaluates the product and start trading with the data provider if the consumer is interested in subscribing the data.

\subsection{Trading}
The whole trading process is shown in Figure \ref{fig:trading_product}. Once a consumer who wants to subscribe the streaming data that is generated in the future pays a subscription fee to the Product Contract, it is added to the consumers list automatically by the smart contract.

\begin{figure}[h]
	\centering
	\includegraphics[width=0.4\textwidth]{trading_product}
	\caption{The process of the product trading.}
	\label{fig:trading_product}
\end{figure}

Next, session key $k$ should be exchanged between data provider and consumers as shown in Figure \ref{fig:key_exchange}. The data provider can obtain public keys of each consumer from the Registration Contract. For each consumer, the data provider encrypts the session key and broker's signature with the consumer's public key and sends the ciphertext $Encrypt(k + Sign(k))$ to the Product Contract. Consumers listen to the smart contract event which is triggered when the ciphertext is updated, and decrypt the ciphertext to get the session key $k$ and signature $Sign(k)$.

@@

\subsection{Refunding}
It is probable that the streaming data sources are delayed or even interrupted after the consumers pay the subscription fee. To protect consumer rights, the subscription fee are not transfered to the data provider until data is generated and published to the MAM channel. If the expected data is not available, consumers can ask for refunds. We assume that less than half of consumers in the Product Contract are irrational and malicious. Each consumer can vote for refunding at any time. If the ratio of consent votes of refunding is higher than the $threshold$ at the $i$th piece of data, the subscription fee is proportionally transfered to the data provider, broker and every consumer. The subscription fee can be prorated as below:

@@

To refund or withdraw subscription fee from the smart contract, data provider, broker, and consumer send a transaction to execute the smart contract and are responsible for transaction fee. We assume that only a half of the expected records are published to the MAM channel. When $F_{b}$ is 5\%, the data provider and broker can withdraw a half of total subscription fee from the smart contract and 5\% of the subscription fee belongs to the broker while the remaining belongs to the data provider. For consumers, they can get a half refund which should be deducted the transaction fee.

@@

\subsection{Game Theory Evaluation}
Game Theory is a methodology to discuss strategic interaciton among game players. If we can ensure Nash Equilibrium of decentralized data marketplace exists at certain acceptable range, then we can promise the sustainability of decentralized data marketplace. Fan Liang et al\cite{SurveyBigDataPricing} listed several different types of game theory models which are applied on data pricing. We choose repeated game to build our game theory model. Repeated game consists of several repetitions of the same base game which meets the scenario of data subscription.

>>>>

\maketitle
\section*{\normalsize\textbf{Abstract}}
Transacting IoT data must be different in many respects to build much-needed trust in data marketplaces, trust that will be key to their sustainability. Data generated internally to an organization is usually not enough to remain competitive, enhance customer experience, and improve strategic decision-making. In this paper, we propose a novel approach to construct IoT-enabled data marketplace by decentralized and trustless architecture, posting the trade records but also including the transaction process on the distributed ledgers. It can efficiently enhance the degree of transparency, since all interactions with smart contracts will be written on-chain. Storage via an end-to-end encrypted message channel allows emitting and accessing trusted data stream over the distributed ledgers regardless of the size or cost of the device, simultaneously making a verifiable Auth-compliant request to the platform. Furthermore, the platform will complete matching, trading and refunding process without the human intervention which also protects the rights of data providers and consumers through a trading policy written on the smart contract, and finally apply evolutionary game theory to the machine economy.
\begin{IEEEkeywords}
    streaming data, crowd sensing, data marketplace, decentralization
\end{IEEEkeywords}

\section{\normalsize\textbf{Introduction}}
The growth of data marketplaces is an inevitable result of the IoT (Internet of Things) revolution. As physical assets such as ships, factories, vehicles, farms and buildings become digital, their digital twins will gradually act as secure data exchanges.\cite{digitaltwin}\cite{AutonomousDriving} As data streams surge across silos and carry value across organizations, traditional value chains will transition into a web of value. This paradigm shift will be more complex to administer, forcing businesses to rethink their competitive play as part of these ecosystems. Data marketplaces will emerge as a means to exchange data, monetize data streams and provide the basis of new business models. We refer to this new wave of value creation, for the Internet of Everything, as the "Economy of Things." There are three main barriers to achieving data marketplace:
\begin{enumerate}
    \item Data owners do not have much control over their data and their data is locked in silos managed by products and services companies.
    \item Data owners only have access to their own data which has little value when it comes to knowledge discovery.
    \item Data owners do not know how to discover knowledge from raw data.
\end{enumerate}

To overcome these barriers, we implemented IoT-enabled data marketplace and sensor data submission functionalities which are intended to be very lightweight and capable of running on embedded devices. They will only need to perform Tangle operations (e.g., producing and consuming secure channels) and communicate with decentralized facilities, which do not rely on single-source network infrastructure. This proposed reference architecture includes functions that could be mapped to different stakeholders, and multiple functions can be implemented by the same administrative stakeholder in a given operational deployment.
\begin{enumerate}
    \item Data Sellers are entities that deploy an IoT infrastructure, for example smart energy meters. These entities are interested in selling the collected data or subsets of that data.
    \item Managed Data Lakes would typically store a massive amount of data and metadata to enable data discovery.
    \item Data Buyers consuming data streams or downloading data sets are interested in the additional value that external data can bring to their internal data.
\end{enumerate}

Take the use case of the Airbox\cite{LASS} for instance. Every household with an Airbox device can collect air quality records automatically and autonomically, rather than passively accept the outcomes from the centralized authorities. To protect privacy, data should be encrypted before on-chain. As for data reliability, we extended the backbone design of the Airbox to interoperate smart-contract-oriented structure to write down every transaction. At the same time, data on-chain will send a verifiable request to mark itself as "being tradeable." This step enables buyers to review and bargain at will. Last but not least, payments will be stored on the smart contracts until the transactions are confirmed. The entire sequence is illustrated in Figure \ref{fig:airbox}.

@@

\section{\normalsize\textbf{Related Work}}
As the economic value of huge amount of data emerges, several researchers have started to explore the design of data marketplace. The Third Party Auditors (TPAs)-based frameworks\cite{TPA} is far from being satisfactory due to the unstandardize data format dynamic nature of IoT data. Therefore, a decentralized data integrity validation and trading process has been proposed in recent years, and distributed ledger technologies (DLTs) is considered a solution, which has the immutable data storage feature that the existence of data can be trusted and no longer rely on any third party authority.

Data Integrity as a Service (DIaaS) is a blockchain-based framework for data integrity proposed by Liu et al.,\cite{DIaas} which is a Cloud Server Service (CSS) and allows both data provider and consumer to validate data integrity by comparing hashes on Ethereum smart contracts\cite{smartContract} and cloud servers. Moreover, Ethereum smart contract can also realize the purchase agreement, including authoriziation and penalization. However, the architecture of DIaaS needs high trust on the CSS. If CSS is malicious or has crashed, losses to both providers and consumers will result. Also, performance analysis shows that IoT devices have low efficiency interacting with Ethereum due to the time-consuming Proof-of-Work(PoW) process.

To address the inefficiency of the Blockchain, \textbf{IOTA}\cite{IOTAwhitepaper} is a cryptocurrency for the IoT industry based on a revolutionary distributed ledger technology, the \textbf{Tangle}, which enables zero-transaction. Based on Tangle, \textbf{Masked Authenticated Messaging(MAM)}\cite{MAM}, is provided for a second layer data communication protocol which allows transmission, access, and verification of an encrypted data stream over the Tangle where privacy and integrity meet.

Based on Tangle and MAM, the IOTA foundation launched a data marketplace\cite{IOTADataMarket} which is suitable for IoT streaming data that not only allows data providers to put data on Tangle without any trusted cloud services, but also allow providers and consumers to trade on Tangle with privacy protected and assurance of data integrity from source with MAM. Nevertheless, the platform design is centralized, new devices require manual approval from the IOTA foundation to be visible in the marketplace. Also, interacting with Tangle is still the bottleneck for low-level devices especially in an unstable network or electrically noisy environment.

A different framework design proposed by Gupta, S.Kanhere and Jurdak\cite{3tierDataMarket} could reduce the burden of low-level devices as mentioned. The infrastructure is a 3-tier decentralized data marketplace architectural design with Ethereum smart contracts which consist of providers, consumers and brokers. The broker is a trustless and highly resourced device that will facilitate the trading of data between the consumer and providers. However, the data integrity and authentication of each participant is still forthcoming.

The sustainability of IoT economic system was under discussion by Dusit Niyato et al.\cite{UtilityStruct}. They evaluated the utility structure of data trading and presented game theory model.  Data marketplace organizers can determine their policies to ensure a sustainable system with the Nash Equilibrium found by game theory and the utility structure. However, refund and subscription mechanism were not mentioned in their work.

Such work proposed different solutions to specific issues of data marketplaces. In this paper, we have an overall design of decentralized data marketplace that handles data integrity and trading procedures, such as buyout and subscibing to future data on distributed ledgers.

\section{\normalsize\textbf{System Architecture}}
Our proposed data marketplace framework is a 3-tier de-centralized architecture with registrars, data providers, data consumers and brokers.

@@

\subsubsection{Registrar}
The registrars are responsible for creating a Registration Contract, which maintains a lookup table of participants, and has the authority to control the participant lists of the decentralized data marketplace.

@@

\subsubsection{Consumer}
Consumers aspire to obtain streaming data to improve the value of their service. However, it is a significant challenge for most consumers to collect the desired data by themselves. So they look to purchasing the streaming data from data providers.

\subsubsection{Broker}
Brokers delegate data providers and consumers to perform computing tasks as brokers are expected to have ample resources. Trustworthy brokers that meet the requirement of the  conformity assessment are added to the decentralized data marketplace. Once a qualified data provider requests to launch a new product, the broker would deal the trading process and publish the their data streams to the MAM channel. For each product, brokerage fees will be charged by the broker.

@@

\subsection{Components}
\subsubsection{Masked Authenticated Messaging}
MAM is a second layer data communication protocol built on the feeless and scalable IOTA network. It resolves the challenges to publish encrypted streaming data to the distributed ledgers with session keys to channel, which indicates that each address is derived from its previous one. In other words, with channel root (aka the first message of a channel) and its session key, all data becomes accessible and validatable. Furthermore, each user can create multiple channels as possible. See Figure \ref{fig:mam_channel}

\begin{figure}[h]
    \centering
    \includegraphics[width=0.4\textwidth]{mam_channel}
    \caption{A user could create multiple MAM channels}
    \label{fig:mam_channel}
\end{figure}

\subsubsection{TangleID}
The TangleID\cite{TangleID} is a self-sovereign identity system based on IOTA that do not require any third-party authority to verify an identity and its digital footprint. With TangleID, the digital footprint is converted into digital assets under the principle of Decentralized Identifiers (DIDs)\cite{DID} defined by W3C. Posting DID documents on MAM makes TangleID a GDPR-Complianced system. Every participant in the data marketplace registers on TangleID, hence one can easily verify data providers' identity to ensure the data persistency from data sources.

\subsubsection{Ethereum Smart Contract}
Smart contract is a protocol for formulating agreement on a blockchain that provides verification and execution of the contract. The code in the smart contract can interact with other contracts, make decisions, store data and transfer cryptocurrency. All conditions and states established in the contract are enforeced with transparency. The appearance of smart contracts meet different requirements of trading pattern.

\subsubsection{Blind Signature}
Blind signature\cite{blindSig} is used to prevent the situation that the a broker would stole data if a session key is not encryted. In fact, blind signature is a form of digital signature where the message is first "blinded" by a random "blinding factor", and then passed to a signer to confirm. The encrypted message, along with the blinding factor, can be later verified with the signer’s public key. In our design, brokers would perform blind signature during the process of adding new products for data providers, in order to send session keys of MAM channel to smart contract without knowing it.

\subsubsection{IPFS}
Inter-Planetary File system(IPFS)\cite{IPFS} is a peer-to-peer network for storing and accessing files, websites, applications, and data in a distributed file system which is not maintained with certain nodes or entities but all IPFS users. In our proposed architecture, brokers are responsible for publishing metadata to IPFS, including titles, data provider information and data preview, in order to provide users with searching capabilities.

\section{\normalsize\textbf{Trading Model}}
In the following, we describe the data trading process in detail and we would use game theory to ensure the sustainability of our tading model. To participate a data marketplace, data providers and consumers have to register first. Then data provider can launch its product on the marketplace. Once a product is launched, it is searchable and can be subsequently traded. The whole trading and refunding process is defined in smart contracts which are easily traceable and irreversible.

The consumer will pay for the data, only when the data sold by the data provider sufficiently accurate, for which we called such data "decent data."
Once the accuracy is lower than a certain threshold, which we call "unacceptable data," the consumers would then consider this data provider as a low quality data provider, and stop buying data from this data provider.

Refunds are a major issue in our research. However, we don't have to take refund as a factor in our game theory model, since in our decentralized data marketplace we use smart contract to store the subscription fee which will be paid to buy the future data. The subscription fee will be paid as new data is transmitted to consumers. In other words, data provider doesn't need to take any procedure to transfer subscription fee from his/her own account to consumers' account. For the same reason, data provider has no responsibility on the refunding processing fee charged by the smart contract as well.

\subsection{Participants Registration}
At the beginning, the registrar creates a Registration Contract, which maintains all participants' information, including their DID documents and public keys. Everyone can query participants' public keys. Those who would like to sell or purchase data may register to become a data provider or consumer. The registrar has the authority to agree with applications. After that, their identities are available in the Registration Contract and the launching and trading processes can begin.

\subsection{Launching and Searching Products}
To sell streaming data, a data provider needs to launch a new product on the data marketplace in advance as shown in Figure \ref{fig:launching_product}. 
MAM allows users to create multiple channels as possible, however, the size of a channel is fixed which is decided before creation. Therefore, data providers should decide how to distribute data product into MAM channels, then determine a trusted broker to create a new MAM channel and Product Contract for recording the participants, subscription price brokerage fee, quantity of data and trading process.

@@

Brokers certify session keys as well. Only one session key can be signed in each product, so data providers cannot fake a session key to deceive consumers. Figure \ref{fig:key_certification} shows the certification process. When a data provider asks a broker to certify new session key $k$, the data provider uses the broker's public key, which is available in the Registration Contract after the broker's registration, as a blinding factor, and the session key is blinded. Then the data provider sends the blinded session key $Blind(k)$ to the broker. The broker signs the message and returns the signature $Sign(Blind(k))$ to data provider. The data provider removes the blinding factor and obtains the broker's signature of the session key, $Sign(k)$, which is verifiable by consumers.

@@

The contract address and product description will be stored in a file which is uploaded to IPFS. Consumers can search the desired product by keywords or tags. The consumer then evaluates the product and initiates the trading with the data provider if the consumer is interested in subscribing to the data.

\subsection{Trading}
The entire trading process is as shown in Figure \ref{fig:trading_product}. Once a consumer who wants to subscribe certain streaming data that is generated in the future pays a subscription fee to the Product Contract, it is added to the consumers list automatically by the smart contract.

\begin{figure}[h]
	\centering
	\includegraphics[width=0.4\textwidth]{trading_product}
	\caption{The process for the product trading.}
	\label{fig:trading_product}
\end{figure}

Next, session key $k$ should be exchanged between the data provider and consumers as shown in Figure \ref{fig:key_exchange}. The data provider can obtain public keys of each consumer from the Registration Contract. For each consumer, the data provider encrypts the session key and broker's signature with the consumer's public key and sends the ciphertext $Encrypt(k + Sign(k))$ to the Product Contract. Consumers listen to the smart contract event which is triggered when the ciphertext is updated, and decrypt the ciphertext to obtain the session key $k$ and signature $Sign(k)$.

@@

\subsection{Refunding}
It is probable that the streaming data sources are delayed or even interrupted after the consumers pay the subscription fee. To protect consumer rights, the subscription fee are not transferred to the data provider until data is generated and published to the MAM channel. If the expected data is not available, consumers can request refunds. We assume that a very small percentage of consumers in the Product Contract are irrational and/or malicious. Each consumer can vote for a refund at any time. If the ratio of consent votes of refunding is higher than the $threshold$ at the $i$th piece of data, the subscription fee is proportionally transferred to the data provider, broker and every consumer. The subscription fee can be prorated as below:

@@

To refund or withdraw subscription fee from the smart contract, data provider, broker, and consumer send a transaction to execute the smart contract and are responsible for transaction fee. We assume that only a half of the expected records are published to the MAM channel. When $F_{b}$ is 5\%, the data provider and broker can withdraw a half of total subscription fee from the smart contract and 5\% of the subscription fee belongs to the broker while the remaining belongs to the data provider. For consumers, they can get half of the subscription fee refunded which should be deducted the transaction fee.

@@

\subsection{Game Theory Evaluation}
Game Theory is a methodology to discuss strategic interaciton among game players. If we can ensure Nash Equilibrium of decentralized data marketplace exists at certain acceptable range, then we can promise the sustainability of decentralized data marketplace. Fan Liang et al\cite{SurveyBigDataPricing} listed several different types of game theory models which are applied on data pricing. We employed repeated game to build our game theory model. Repeated game consists of several repetitions of the same base game which meets the scenario of data subscription.
